Evaluate residuals in each cohort and brain region

### 2020-11-18 combined_analysis/eval_resid_in_each.Rmd
Initial commit

library(ggplot2)
library(dplyr)
library(ComplexHeatmap)
library(readxl)
library(gtools)
library(corrplot)
library(pvclust)
library(metafor)
library(data.table)
library(cowplot)
library(kableExtra)
library(githubr)
library(ggrepel)
library(knitr)
library(patchwork)
library(plyr)
library(compositions)
library(BiocParallel)

@@

asdfas

residMat.lst = lapply( names(dge.lst), function(datID){

@@

  # get formula
  j = unlist(sapply(names(form.lst), function(x) grep(x, datID)))
  form_use = form.lst[[names(j)]]

  # add these terms back into the model
  form_add = ifelse(names(j) == "MSSM-Penn-Pitt",
        ~ Dx + Reported_Gender + Institution*(cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3),
        ~ Dx + Reported_Gender + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

  # apply voom
  vobj = voomWithDreamWeights(dge, form_use, info, save.plot=TRUE, BPPARAM = SnowParam(18))

@@

  })
names(residMat.lst) = names(dge.lst)
```

```{r run.peer}

  model = PEER()

  PEER_setPhenoMean(model,as.matrix(expr))

  PEER_setCovariates(model, as.matrix(covs))

  PEER_setNk(model,10)

  latentVariables = PEER_getX(model)

```

>>>>

library(ggplot2)
library(dplyr)
library(ComplexHeatmap)
library(readxl)
library(gtools)
library(corrplot)
library(pvclust)
library(metafor)
library(data.table)
library(peer)
library(cowplot)
library(kableExtra)
library(githubr)
library(ggrepel)
library(knitr)
library(patchwork)
library(plyr)
library(compositions)
library(BiocParallel)

@@

for( datID in names(dge.lst) ){

@@

  # get formula
  j = unlist(sapply(names(form.lst), function(x) grep(x, datID)))
  form_use = form.lst[[names(j)]]
  # apply voom
  vobj = voomWithDreamWeights(dge[1:200,], form_use, info, save.plot=TRUE, BPPARAM = SnowParam(18))

  # construct covariate matrix
  cov_matrix = model.matrix(form_use, info)

  # fit PEER
  model = PEER()

  PEER_setPhenoMean(model, t(vobj$E))

  PEER_setCovariates(model, cov_matrix)

  PEER_setNk(model,2)

  # extract PEER latent variables
  # first ncol(cov_matrix) columns are the oringal covariates
  latentVariables = PEER_getX(model)[,-c(1:ncol(cov_matrix))]
  rownames(latentVariables) = rownames(cov_matrix)
  colnames(latentVariables) = paste0("PEER_", 1:ncol(latentVariables))

  # upload observed expression
  file = paste0('geneExpr_',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
  storeData( vobj$E, file, paste0(datID, " Observed expression as log2 CPM"))

  # upload covariate matrix
  file = paste0('covariateMatrix_',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
  storeData( cov_matrix, file, paste0(datID, " Covariates for QTL analysis"))

  # upload latent variables
  file = paste0('metadata_',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
  storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis"))
}
```

For each cohort and each brain region, compute TMM normalization, log2 CPM with voomWithDreamWeights, and a set of covariates.  Then compute PEER components using the observed expression and the covariates

    `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3

  # add these terms back into the model
  form_add = ifelse(names(j) == "MSSM-Penn-Pitt",
        '~ Dx + Reported_Gender + Institution*(cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)',
       ' ~ Dx + Reported_Gender + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3')
  form_add = as.formula(form_add)

@@

  })
names(residMat.lst) = names(dge.lst)
--->
